### 2021-01-06 paper/localpsf.tex
trying to clarify dirac comb discussion

After discretization (see Appendix \ref{app:discretized_operations}), the operator $\mathcal{A}$ becomes a dense matrix, $\mathbf{A}$, that is typically too large to be built and stored. The first property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\mathbf{A}$ and $\mathbf{A}^T$ with arbitrary vectors, but one cannot easily access matrix entries $\mathbf{A}_{ij}$. In the matrix-free regime, to compute $\mathbf{A}_{ij}$ one could compute $\mathbf{v} = \mathbf{A}\mathbf{e}_j$, then extract the $i^\text{th}$ entry, $\mathbf{A}_{ij} = \mathbf{v}_i$. However, this process is wasteful because one computes the entire vector $\mathbf{v}$, then discards all but one component. Here $\mathbf{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero. In PDE constrained optimization and inverse problems, Hessians are typically available matrix free; we do not have direct access to these operators, but we can apply them to vectors via a process that involve solving two PDEs \cite{HESSIANADJOINT}. More broadly, $\mathbf{A}$ is matrix-free if $\mathbf{A}$ is defined implicitly via its action on vectors, and the process of applying $\mathbf{A}$ to a vector requires performing a nontrivial computational procedure, such as solving a large linear system, or timestepping.

@@

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i \in H^2(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$ with pure Neumann boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness \cite{JACOBSEN}, the function $w_i$ is the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.

>>>>

After discretization (see Appendix \ref{app:discretized_operations}), the operator $\mathcal{A}$ becomes a dense matrix, $\mathbf{A}$, that is typically too large to be built and stored. The first property is called ``matrix-free'' because at the discrete level it means that one can perform matrix-vector products of $\mathbf{A}$ and $\mathbf{A}^T$ with arbitrary vectors, but one cannot easily access matrix entries $\mathbf{A}_{ij}$. In the matrix-free regime, to compute $\mathbf{A}_{ij}$ one could compute $\mathbf{v} = \mathbf{A}\mathbf{e}_j$, then extract $\mathbf{A}_{ij} = \mathbf{v}_i$. However, this process is wasteful because one computes the entire vector $\mathbf{v}$, then discards all but one component. Here $\mathbf{e}_j=(0,\dots,0,1,0,\dots,0)$ is the unit vector which has $j^\text{th}$ component equal to one and all other components equal to zero. In PDE constrained optimization and inverse problems, Hessians are typically available matrix free; we do not have direct access to Hessian matrix entries, but the implicit function theorem allows us to apply the Hessian to a vector via a process that involves solving two PDEs \cite{HESSIANADJOINT}. More broadly, $\mathbf{A}$ is matrix-free if $\mathbf{A}$ is defined implicitly via its action on vectors, and the process of applying $\mathbf{A}$ to a vector requires performing a nontrivial computational procedure, such as solving a large linear system, or timestepping.

@@

We choose the weighting functions, $w_i$, to be the solutions to the following optimization problems:
\begin{equation}
\label{eq:wi_optimization_problem_intro}
\begin{aligned}
\min_{w_i \in H^2_N(\Omega)} &\quad \frac{1}{2}\norm{\Delta w_i}_{L^2(\Omega)}^2 \\
\text{such that} &\quad w_i(x_j) = \delta_{ij}, \quad j=1,\dots,q.
\end{aligned}
\end{equation}
Here $\Delta$ is the Laplacian on $\Omega$, $H^2_N(\Omega)$ is the space of all functions in the Sobolev space $H^2(\Omega)$ with Neumann zero boundary conditions, and the right hand side of the constraint, $\delta_{ij}$, is the Kronecker delta, which takes value one if $i=j$ and zero if $i \neq j$. Since the Laplacian measures local deviation from flatness \cite{JACOBSEN}, the function $w_i$ is the flattest function, in a least-squares sense, that takes the value one at the sample point $x_i$, and the value zero at the other sample points $x_j$, $i \neq j$. Computing the weighting functions $w_i$ requires solving two Poisson PDEs per weighting function, and these PDEs are solved cheaply using multigrid. We call this interpolation scheme \emph{Poisson interpolation}. The advantage of Poisson interpolation over other interpolation methods, most notably radial basis function interpolation \cite{ESCANDE}, is that Poisson interpolation incorporates information about the domain geometry when constructing the weighting functions. This is illustrated in Figure FIG.
